%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                                                      %
%     File: Thesis_Acknowledgments.tex                                 %
%     Tex Master: Thesis.tex                                           %
%                                                                      %
%     Author: Andre C. Marta                                           %
%     Last modified :  2 Jul 2015                                      %
%                                                                      %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section*{\acknowledgments}

% Add entry in the table of contents as section
\addcontentsline{toc}{section}{\acknowledgments}

To the ones at IPP. Especially to Elisabeth Wolfrum and to Garrard Conway, for their guidance and support. To the divertor gang: Steffen, Felix and Matthias. Thanks for all your help, support and giving reflectometry a chance.

To the Scientific Spetsnaz, for always giving me tea and chocolate in the rainier days.

To the Ref team. To Sylvie, for all the amazing effort she put at the beginning of this work. To Meneses, sem makas, tranquilo, oi, tu queres lá ver? To Silva for trusting me to pilot his baby for all these years. To Jorge, thanks for your work ethic and for always being stubborn. To Filipe, thanks for teaching me that a little bit of culture is always good but never enough (and helping me release the clown that one time). To malenkaya podruga Valentina, for being a part-time babushka in Germany. To Diogo, the Robin to my Batman.

To my advisor, Carlos. Thanks for all the support and hard work you have put into the Reflectometry group. I hope I can repay your efforts in the form of papers. 

To my friends. Neves, Ferras, Paulo, Nuno, Paulo, David, Ovos, Kurta and Ed: thanks for being unwilling test subjects to all my bad jokes.

To Mãe Brandão and Pai Brandão for all the support, patience and gins.

To my family. To Méne, for teaching me talent is never a substitute to hard work. To Bé, thanks for all your efforts and sacrifices in trying to make me and my brother the best we could ever be, but we were a lost cause to begin with. To Pica, for showing me you can do anything when you have the drive for it. To Quim and Glória, for teaching me that giving is the greatest legacy. To Fex, for knowing.

And finally, to Susana. You know what you did.

\vspace{5mm}

This work has been carried out within the framework of the EUROfusion Consortium and has received funding from the Euratom research and training programme 2014-2018 under grant agreement No 633053. IST activities also received financial support from ``Funda\c{c}\~ao para a Ci\^{e}ncia e Tecnologia'' through project $UID/FIS/50010/2013$ and grant $SFRH/BD/87738/2012$. The views and opinions expressed herein do not necessarily reflect those of the European Commission.

\begin{flushright}
Muito obrigado.

Luís
\end{flushright}